\documentclass[12pt]{article}
\usepackage{acronym}
\usepackage{titling}
\usepackage[small,compact]{titlesec}
\usepackage{enumitem}
\usepackage[margin=1.25in]{geometry}

\pagenumbering{gobble}

\setlist{nolistsep}

\title{MiniJava LLVM Proposal}
\author{Mitch Souders and Mark Smith}
\date{May 2, 2014}
\begin{document}

\makeatletter
\def\maketitle{\par{\centerline{\huge\bfseries\@title}}\par\@author -- \@date}
\makeatother

\maketitle

\section*{Project Topic}
The primary goal of this project is to gain familiarity with \texttt{LLVM}. The proposal is to create an implementation for compiling MiniJava to the \texttt{LLVM} runtime IR.  The basis for the starting framework will be the MiniJava application used in CS321/322.  The compiler starter framework was provided by Professor Mark Jones.  The MiniJava project currently includes options for running as an interpreter or compiling to x86 code.

Proposed project flow:
\begin{enumerate}
\item Convert base MiniJava to \texttt{LLVM} IR.

    MiniJava already requires (among other things):
    \begin{itemize}
    \item Classes, Variables, Statements, Loops, Branches, etc.
    \item Arrays
    \item Object Methods/Fields
    \item Static Methods/Fields
    \item Dynamic Dispatch (polymorphic methods)
    \end{itemize}
\item Extend MiniJava to a larger subset of Java
    \begin{itemize}
    \item Interfaces
    % I feel like there should be more here
    % but MiniJava already seems to have a lot
    % of base requirements.
    \end{itemize}
\item \texttt{LLVM} Garbage Collection
\end{enumerate}

\section*{Deliverables}
The project deliverables will be a summary of the work, highlights of knowledge gained from implementation, the completed compiler as Java source code and unit tests indicating correct operations for language construct snippets.

\section*{Materials}
The following tools will be used to implement this project. Note: Some of these tools have alternates that could be used if the specified tool prove unsuitable (e.g. using \texttt{llvm-j} instead of \texttt{jllvm}).

\begin{description}
\item[MiniJava Compiler]
	The MiniJava Compiler (\texttt{MJC}) from CS321/322 will be considered the base version of the language MiniJava with further extensions added as required.

\item[LLVM]\footnote{http://llvm.org/} The target compiler for the generated IR for MiniJava.

\item[jllvm]\footnote{https://code.google.com/p/jllvm}
Java bindings to \texttt{LLVM}, which allow direct interaction with \texttt{LLVM}.

\end{description}

\end{document}
